\documentclass[11pt,a4paper]{moderncv}
\usepackage[T2A]{fontenc}
\usepackage[english, russian] {babel}
\usepackage[utf8]{inputenc}

\moderncvstyle{classic}
\moderncvcolor{blue}
\renewcommand{\rmdefault}{cmr}
\usepackage[scale=0.75]{geometry}

% personal data
\firstname{Ivan}
\familyname{Kotenkov}
\mobile{+420777001876}
\email{ivan.kotenkov@gmail.com}

\begin{document}
\makecvtitle

\section{Experience}
\cventry{Sep 2014 -- present}{Senior Software Engineer}{\textbf{Yandex}}{Moscow}{}{Development of Yandex.Browser's rendering engine.}
\cventry{Jul 2013 -- Aug 2014}{Software Engineer}{\textbf{Yandex}}{Moscow}{}{Development of Yandex.Browser's rendering engine.
\begin{itemize}%
\item Participated in development of almost all Yandex.Browser features concerning rendering engine: in-page search, different APIs, selection, editing, etc.
\item Landed multiple patches to Chromium.
\item Conducted regular code reviews.
\item Conducted multiple coding intreviews.
\end{itemize}
}
\cventry{Aug 2010 -- Jun 2013}{Software Engineer}{\textbf{Lianozovo Electromechanical Plant}}{Moscow}{}{Development of air traffic control systems.
\begin{itemize}%
\item Developed an internal library for 3d object intersection detection.
\item Developed a program for 3d object visualization.
\item Built a connection between two systems using ASTERIX protocol.
\end{itemize}
}
\cventry{Jul 2012 -- Feb 2013}{Remote C++ developer}{\textbf{SimplyCeph}}{}{}{Wrote a program for modifying STL(STereoLithography) models - automated removal of unnecessary parts, hole searching.}

\section{Technical skills}
\cvlistitem{\textit{Programming languages}: C++, C, Python}
\cvlistitem{\textit{Libraries}: STL, QT}
\cvlistitem{\textit{Operating systems}: linux, mac os}
\cvlistitem{\textit{Version control}: git, svn}
\cvlistitem{\textit{Other}: gdb, lldb, vim, bash, tex}

\section{Education}
\cventry{2005 -- 2012}{Specialist degree}{Moscow State University}
  {\newline\textit{Department}: mechanics and mathematics}
  {\newline\textit{Specialization}: applied mathematics}{}

\section{Languages}
\cvitemwithcomment{Russian}{Native}{}
\cvitemwithcomment{English}{Upper intermediate}{}
\cvitemwithcomment{Czech}{Upper intermediate}{}

\renewcommand{\listitemsymbol}{-~}

\end{document}
